Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-04-21 ms.tex
outflows

The accretion rate onto the SMBH is given by the total mass loss rate interior to the stagnation radius (eq.~[\ref{eq:q}]), 
\begin{eqnarray}
  \dot{M} &=& 4\pi \int_{0}^{r_{s}}q r^{2}dr = \frac{\eta M_{\star}|_{r_{\rm s}}}{\th} \nonumber \\
&\approx&
  \begin{cases}
    4.5 \times 10^{-5} M_{\bullet,8}^{1.76}
    v_{500}^{-3.8}  \eta_{0.02} \Msun \, \pyear& \text{core} \\
    3.2 \times 10^{-5} M_{\bullet,8}^{1.48} 
    v_{500}^{-2.4}  \eta_{0.02} \Msun \, \pyear  & \text{cusp}, 
  \end{cases}
  \label{eq:mdot_analytic}
\end{eqnarray}
where we have assumed $v_{w} \gg \sigma_0$ by adopting equation
(\ref{eq:stag_simple}) for $r_s$.  The resulting Eddington ratio is
given by
\begin{eqnarray}
\frac{\dot{M}}{\dot{M}_{\rm edd}} &\approx&
  \begin{cases}
    2.0 \times 10^{-5} M_{\bullet,8}^{0.76}
    v_{500}^{-3.8}  \eta_{0.02}   & \text{core}, \\
    1.4 \times 10^{-5} \Mbheight^{0.48} 
    v_{500}^{-2.4}  \eta_{0.02}   & \text{cusp}, 
  \end{cases}
  \label{eq:eddr_analytic}
\end{eqnarray}
where $\dot{M}_{\rm edd} = 2.6M_{\bullet,8}M_{\odot}$ yr$^{-1}$ is the
Eddington accretion rate, assuming a radiative efficiency of ten per
cent.  Note the sensitive dependence of the accretion rate on the wind
heating rate.
%To reproduce the estimated values $\dot{M}/\dot{M}_{\rm edd} \lesssim 10^{-3}$ in low-luminosity AGN or quiescent galaxies, we thus require $v_{w} \gtrsim 150M_{\bullet,8}^{0.5}$

@@

\item  The accretion rates of early-type galaxies are below the maximum value for thermally stable flow, $\dot{M}_{\rm TI}$ (Fig.~\ref{fig:miller}), only for high X-ray radiative efficiencies, similar to the maximum values predicted by ADAF models.  Therefore the current X-ray detections could instead be comprised mostly of nuclei undergoing non-steady accretion due to thermal instabilities.  In this case there may exist a separate branch of low-$L_X$ (undetected) thermally-stable nuclei, especially at low $M_{\bullet}$.  Such a bimodal population would call into question methods of extrapolating the $L_{\rm X}(M_{\bullet}$) relationship to low $M_{\bullet}$ in order to constrain the SMBH occupation fraction in low mass galaxies (\citealt{Miller+15}).

>>>>

The accretion rate onto the SMBH is given by the total mass loss rate interior to the stagnation radius (eq.~[\ref{eq:q}]), 
\begin{eqnarray}
  \dot{M} &=& 4\pi \int_{0}^{r_{s}}q r^{2}dr = \frac{\eta M_{\star}|_{r_{\rm s}}}{\th} \nonumber \\
&\approx&
  \begin{cases}
    4.5 \times 10^{-5} M_{\bullet,8}^{1.76}
    v_{500}^{-3.8}  \eta_{0.02} \Msun \, \pyear& \text{core} \\
    3.2 \times 10^{-5} M_{\bullet,8}^{1.48} 
    v_{500}^{-2.4}  \eta_{0.02} \Msun \, \pyear  & \text{cusp}, 
  \end{cases}
  \label{eq:mdot_analytic}
\end{eqnarray}
where we have assumed $v_{w} \gg \sigma_0$ by adopting equation
(\ref{eq:stag_simple}) for $r_s$.  The resulting Eddington ratio is
given by
\begin{eqnarray}
\frac{\dot{M}}{\dot{M}_{\rm edd}} &\approx&
  \begin{cases}
    2.0 \times 10^{-5} M_{\bullet,8}^{0.76}
    v_{500}^{-3.8}  \eta_{0.02}   & \text{core}, \\
    1.4 \times 10^{-5} \Mbheight^{0.48} 
    v_{500}^{-2.4}  \eta_{0.02}   & \text{cusp}, 
  \end{cases}
  \label{eq:eddr_analytic}
\end{eqnarray}
where $\dot{M}_{\rm edd} = 2.6M_{\bullet,8}M_{\odot}$ yr$^{-1}$ is the
Eddington accretion rate, assuming a radiative efficiency of ten per
cent.  Note the sensitive dependence of the accretion rate on the wind
heating rate. Also, we emphasize that
equation~\eqref{eq:eddr_analytic} represents the mass inflow rate on
large scales and does not include small scale outflows. In reality, only
a fraction $\alpha$ (the standard Shakura-Sunyaev parameter--assumed
to be 0.1) will make it down to the black hole \citep{Li+2013}.

@@

\item The accretion rates of early-type galaxies are below the maximum
  value for thermally stable flow, $\dot{M}_{\rm TI}$
  (Fig.~\ref{fig:miller}), only for high X-ray radiative efficiencies.
  Therefore the current X-ray detections could instead be comprised
  mostly of nuclei undergoing outburst due to thermal instabilities.
  In this case there may exist a separate branch of low-$L_X$
  (undetected) thermally-stable nuclei, especially at low
  $M_{\bullet}$.  Such a bimodal population would call into question
  methods of extrapolating the $L_{\rm X}(M_{\bullet}$) relationship
  to low $M_{\bullet}$ in order to constrain the SMBH occupation
  fraction in low mass galaxies (\citealt{Miller+15}).
